\documentclass[10pt]{article}

%opening
\title{
	{A CONCEPT PAPER ON THEFTY IN NKRUMAH HALL}\\
}
\author{
{MAGERO TIMOTHY 215014313   15/U/7296/PS}
}
\begin{document}
\title{	{A CONCEPT PAPER ON THEFTY IN NKRUMAH HALL}\\}
\maketitle

\

\

\section{INTRODUCTION}
{The principal objective of this study is to examine the issue of rapant theft inside the osagefo land nkrumah hall. Nkrumah Hall is one of the great halls in makerere university .it a child to big hall which was named as north courte.Nkrumah Hall is faced by alots of problems such as stealing .Theft refers to taking somebodys property without his concern .This causes student to fail exams since some their materials used in learning are stolen and also stress comes along .Stealing leads to death at a certain moment especially when the person caught in act of stealing property..}
\section{BACKGROUND TO THE PROBLEM}
{Nkrumah Hall has witnessed incidents of thefty including Mob justice, loss of money and failing of exams, breaking of doors, computers or computer accessories, phones, cameras, laptops to students’ property from halls of residence.Other incidents include shame including like removing of clothes of the suspected person of stealing. On the issue of mob justice ,in 2014 a student was killed at Nkrumah hall by his fellow students who suspected him .This lead to arrest of 3 students who were taken to luzira and until now the issue is still in court.
}
\section{PROBLEM STATEMENT}
{My study mainly focuses on thefty in a perspective of a unique population in Nkrumah Hall.The purpose of this research is to confront this serious  issue of thefty through analyzing people stolen from, what is stolen from them, methodological problems with collecting thefty data, underlying issues related to thefty, and promising practices to prevent and address thefty.
}
\section{METHODOLOGY}
{I intend to use the electronic data collection forms, interviews and review literation of the collected data from various sources about the growing syndrome of thefy in most Halls around the University. The collected data will be subjected to analysis to ensure consistency and efficiency.The data to be collected will include images of Nkrumah Hall as well as recordings of conversations between me and various students i interact with in Nkrumah Hall inorder to keep track of information from first hand sources. I will use ODK build to create electronic data collection forms which i wiil upload to my phone to be used during data collection through ODK collect installed on my Android device. The collected data will be stored on ODK aggregate server configured on my computer and will be fully analyzed, assessed and stored to facilitate future research and findings on thefy in Nkrumah Hall.}
\section{OUTCOMES}
{I highly anticipate to get the results out of my research that I am going to
	undertake. As clearly specified I will collect all the data using ODK collect on
	my android device and the data will be stored on the aggregate server. The outcomes
	of this research will facilitate further solutions to thefty in Nkrumah Hall.
}
\section{REFERENCES}
{WARDEN NKRUMAH HALL,  
DEAN OF STUDENTS MAKERERE UNIVERSITY,  
CHAIRMAN NKRUMAH HALL}

\end{document}


