\documentclass[10pt]{article}

%opening
\title{
	{A REPORT ON  THEFTY IN NKRUMAH HALL}\\
}
\author{
{MAGERO TIMOTHY 215014313   15/U/7296/PS}
}
\begin{document}
\title{	{A REPORT ON THEFTY IN NKRUMAH HALL}\\}
\maketitle

\

\

\section{INTRODUCTION}
{Thefty  can be defined in many persepectives ranging from stealing, copying in exams, hacking of university servers. Thefty in particular is an act of taking of someones property without his notice that results in mob justice, death, psychological harm and maldevelopment. This has been a general issue of recent in Nkrumah Hall but the Nkrumah Hall management together with concerned parties like police have done their best to curb the vice out of its territories. This report paper consists of the methodology section, my findings i obtained from the data i collected ,conclusions together with the recommendations.}

\section{FINDINGS}
{According to the people i interacted with around Nkrumah Hall, I found out many students have been victims of circumstances of Thefty. Most of the cases I recorded were thefty most especially rooms in Nkrumah for resident students and the other issue was on Non residents in Hostels. Futhermore I found out that this brings about emotional or psychological injury in one way or and greatly affects their academics standards and a barrier to their careers.
}

\section{METHODOLOGY}
{I interacted with many people on the issue of thefty in Nkrumah Hall.I asked questions ranging from their knowledge about the vice to their experiences if any of them have been victims of this syndrome. I recorded my conversation with them and many were very cooperative and there responses were unbiased. I also took out photos of  the respondents as you can really see below are some of the respondents i managed to interact with on the issue of thefty in Nkrumah Hall.}


\section{CONCLUSIONS}
{Thefty should be stopped in Halls of residence so that students can have better environments for academics.
}

\end{document}


